---
title: "stuff for anson and anthony"
author: "Levi"
date: "2023-08-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load required libraries
library(tidyverse)
library(lubridate)
library(haven)
library(sjlabelled)
library(countrycode)
library(ggplot2)
library(lme4)
library(lmerTest)
library(sjPlot)
library(htmltools)
library(interactions)
library(multcomp)
library(Hmisc)

# Set options for numeric output
options(scipen = 9999) 

# Set directory (Windows)
# setwd('/Documents/Work/University/PhD in Psychology (University of Toronto)/PhD Work/Data/Analysis')
```

## Create function that can create dataframes of the joint hypothesis tests

```{r}
joint_hypothesis_df <- function(identifier_name, ...) {
  # Convert a single summary object to a data frame
  convert_to_df <- function(summary_object, id_name) {
    data.frame(
      Identifier = id_name,
      Estimate = summary_object$test$coefficients,
      Std.Error = summary_object$test$sigma,
      z.value = summary_object$test$tstat,
      p.value = format.pval(summary_object$test$pvalues, digits = 20, eps = .Machine$double.eps)
    )
  }
  # Extract the summary objects from the ...
  summary_objects <- list(...)
  # Check if lengths match
  if(length(summary_objects) != length(identifier_name)) {
    stop("Length of identifier names does not match the number of summary objects provided.")
  }
  names(summary_objects) <- identifier_name
  # Convert each summary object to a data frame and combine
  combined_df <- do.call(rbind, lapply(names(summary_objects), function(name) {
    convert_to_df(summary_objects[[name]], name)
  }))
  return(combined_df)
}
```

##### Run joint hypothesis test to see if any groups from part_freedom differed from 0 (years_after_eu and years_before_after_eu, life satisfaction)

This is a continuous variable (part_freedom, which serves as our moderator).

```{r}
# Load data and model
load('data_eu_ls_part_freedom.RData')
load('analysis_eu_ls_part_freedom.RData')

# Set up matrix for high, mean, and low part_freedom effect
coefeq_high <- matrix(data = 0, nrow = 1, ncol = length(fixef(analysis_eu_ls_part_freedom)))
coefeq_mean <- matrix(data = 0, nrow = 1, ncol = length(fixef(analysis_eu_ls_part_freedom)))
coefeq_low <- matrix(data = 0, nrow = 1, ncol = length(fixef(analysis_eu_ls_part_freedom)))

# Set names for part_freedom matrices
colnames(coefeq_high) <- names(fixef(analysis_eu_ls_part_freedom))
colnames(coefeq_mean) <- names(fixef(analysis_eu_ls_part_freedom))
colnames(coefeq_low) <- names(fixef(analysis_eu_ls_part_freedom))

# Set value of post_eu_status1 to be 1 (thereby indicating it occurs after a country joins the European Union)
coefeq_high[1, "post_eu_status1"] <- 1
coefeq_mean[1, "post_eu_status1"] <- 1
coefeq_low[1, "post_eu_status1"] <- 1

# Set value of moderator:post_eu_status1 interaction, with the value set as the appropriate standard deviation of part_freedom
coefeq_high[1, "moderator:post_eu_status1"] <- 1
coefeq_mean[1, "moderator:post_eu_status1"] <- 0
coefeq_low[1, "moderator:post_eu_status1"] <- -1

# Set value of years_after_eu to be 10 (thereby indicating testing after a country has been in the European Union for 10 years)
coefeq_high[1, "years_after_eu"] <- 10
coefeq_mean[1, "years_after_eu"] <- 10
coefeq_low[1, "years_after_eu"] <- 10

# Set value of moderator:years_after_eu interaction, with the value set as 10 x the value of part_freedom sd
coefeq_high[1, "moderator:years_after_eu"] <- 10
coefeq_mean[1, "moderator:years_after_eu"] <- 0
coefeq_low[1, "moderator:years_after_eu"] <- -10

# Set value of years_before_after_eu to be 10 (thereby indicating testing after a country has been in the European Union for 10 years)
coefeq_high[1, "years_before_after_eu"] <- 10
coefeq_mean[1, "years_before_after_eu"] <- 10
coefeq_low[1, "years_before_after_eu"] <- 10

# Set value of years_before_after_eu:moderator interaction, with the value set as 10 x the value of part_freedom sd
coefeq_high[1, "years_before_after_eu:moderator"] <- 10
coefeq_mean[1, "years_before_after_eu:moderator"] <- 0
coefeq_low[1, "years_before_after_eu:moderator"] <- -10

# Run the joint hypothesis test
sdhigh_ls_part_freedom_aftereu <- glht(model = analysis_eu_ls_part_freedom, linfct = coefeq_high, rhs = 0, alternative = "greater")
sdmean_ls_part_freedom_aftereu <- glht(model = analysis_eu_ls_part_freedom, linfct = coefeq_mean, rhs = 0, alternative = "greater")
sdlow_ls_part_freedom_aftereu <- glht(model = analysis_eu_ls_part_freedom, linfct = coefeq_low, rhs = 0, alternative = "greater")

# Create summary objects in prepartion for the dataframe
sdhigh_ls_part_freedom_aftereu <- summary(sdhigh_ls_part_freedom_aftereu)
sdmean_ls_part_freedom_aftereu <- summary(sdmean_ls_part_freedom_aftereu)
sdlow_ls_part_freedom_aftereu <- summary(sdlow_ls_part_freedom_aftereu)

# Create the dataframe
joint_ls_part_freedom_aftereu <- joint_hypothesis_df(c("High freedom", "Mean freedom", "Low freedom"), sdhigh_ls_part_freedom_aftereu, sdmean_ls_part_freedom_aftereu, sdlow_ls_part_freedom_aftereu) %>%
  rename("After EU" = Identifier)

# Save dataframe
save(joint_ls_part_freedom_aftereu, file = 'joint_ls_part_freedom_aftereu.RData')

# Remove dataframe
rm(data_eu_ls_part_freedom, analysis_eu_ls_part_freedom, joint_ls_part_freedom_aftereu, sdhigh_ls_part_freedom_aftereu, sdmean_ls_part_freedom_aftereu, sdlow_ls_part_freedom_aftereu)
```

##### Run joint hypothesis test to see if any groups from part_income_wvs_subj differed from 0 (years_after_eu and years_before_after_eu, life satisfaction)

This is a categorical variable (part_income_wvs_subj, which serves as our moderator).

```{r}
# Load data and model
load('data_eu_ls_part_income_wvs_subj.RData')
load('analysis_eu_ls_part_income_wvs_subj.RData')

# Set up matrix for high, mean, and low part_income_wvs_subj effect
coefeq_2 <- matrix(data = 0, nrow = 1, ncol = length(fixef(analysis_eu_ls_part_income_wvs_subj)))
coefeq_1 <- matrix(data = 0, nrow = 1, ncol = length(fixef(analysis_eu_ls_part_income_wvs_subj)))
coefeq_0 <- matrix(data = 0, nrow = 1, ncol = length(fixef(analysis_eu_ls_part_income_wvs_subj)))

# Set names for part_income_wvs_subj matrices
colnames(coefeq_2) <- names(fixef(analysis_eu_ls_part_income_wvs_subj))
colnames(coefeq_1) <- names(fixef(analysis_eu_ls_part_income_wvs_subj))
colnames(coefeq_0) <- names(fixef(analysis_eu_ls_part_income_wvs_subj))

# Set value of post_eu_status1 to be 1 (thereby indicating it occurs after a country joins the European Union)
coefeq_2[1, "post_eu_status1"] <- 1
coefeq_1[1, "post_eu_status1"] <- 1
coefeq_0[1, "post_eu_status1"] <- 1

# Set value of moderator:post_eu_status1 interaction, with the value set as the appropriate value of part_income_wvs_subj
coefeq_2[1, "moderator2:post_eu_status1"] <- 1
# coefeq_1[1, "post_eu_status1"] <- 1 # This is the pattern for the reference group
coefeq_0[1, "moderator0:post_eu_status1"] <- 1

# Set value of years_after_eu to be 10 (thereby indicating testing after a country has been in the European Union for 10 years)
coefeq_2[1, "years_after_eu"] <- 10
coefeq_1[1, "years_after_eu"] <- 10
coefeq_0[1, "years_after_eu"] <- 10

# Set value of moderator:years_after_eu interaction, with the value set as 10 x the value of part_income_wvs_subj
coefeq_2[1, "moderator2:years_after_eu"] <- 10
# coefeq_1[1, "years_after_eu"] <- 10 # This is the pattern for the reference group
coefeq_0[1, "moderator0:years_after_eu"] <- 10

# Set value of years_before_after_eu to be 10 (thereby indicating testing after a country has been in the European Union for 10 years)
coefeq_2[1, "years_before_after_eu"] <- 10
coefeq_1[1, "years_before_after_eu"] <- 10
coefeq_0[1, "years_before_after_eu"] <- 10

# Set value of years_before_after_eu:moderator interaction, with the value set as 10 x the value of part_income_wvs_subj
coefeq_2[1, "years_before_after_eu:moderator2"] <- 10
# coefeq_1[1, "years_before_after_eu"] <- 10 # This is the pattern for the reference group
coefeq_0[1, "years_before_after_eu:moderator0"] <- 10

# Run the joint hypothesis test
sd2_ls_part_income_wvs_subj_aftereu <- glht(model = analysis_eu_ls_part_income_wvs_subj, linfct = coefeq_2, rhs = 0, alternative = "greater")
sd1_ls_part_income_wvs_subj_aftereu <- glht(model = analysis_eu_ls_part_income_wvs_subj, linfct = coefeq_1, rhs = 0, alternative = "greater")
sd0_ls_part_income_wvs_subj_aftereu <- glht(model = analysis_eu_ls_part_income_wvs_subj, linfct = coefeq_0, rhs = 0, alternative = "greater")

# Create summary objects in prepartion for the dataframe
sd2_ls_part_income_wvs_subj_aftereu <- summary(sd2_ls_part_income_wvs_subj_aftereu)
sd1_ls_part_income_wvs_subj_aftereu <- summary(sd1_ls_part_income_wvs_subj_aftereu)
sd0_ls_part_income_wvs_subj_aftereu <- summary(sd0_ls_part_income_wvs_subj_aftereu)

# Create the dataframe
joint_part_income_wvs_subj_aftereu <- joint_hypothesis_df(c("High subjective income", "Medium subjective income", "Low subjective income"), sd2_ls_part_income_wvs_subj_aftereu, sd1_ls_part_income_wvs_subj_aftereu, sd0_ls_part_income_wvs_subj_aftereu) %>%
  rename("After EU" = Identifier)

# Save dataframe
save(joint_part_income_wvs_subj_aftereu, file = 'joint_part_income_wvs_subj_aftereu.RData')

# Remove dataframe
rm(data_eu_ls_part_income_wvs_subj, analysis_eu_ls_part_income_wvs_subj, joint_part_income_wvs_subj_aftereu, sd2_ls_part_income_wvs_subj_aftereu, sd1_ls_part_income_wvs_subj_aftereu, sd0_ls_part_income_wvs_subj_aftereu)
```
